Order reduction and partial MILP models \\ for certifying Robustness of DNNs globally.

### 2025-07-28 AAAI2026/Lipitschz.tex
update
lip
adjust the tables

	\hspace*{-10ex}
	\begin{tikzpicture}
		\begin{axis}[	axis on top, xlabel = \(x'_i\),
			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
			set layers=default,
			xmax = 4, xmin = -4,
			ymax = 1, ymin = -1,		
			zmax = 1, zmin = -1,
			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
			xticklabels = {$0$}, ztick   = {-1,0,1},
			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
			view={35}{14},
			]
			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
			coordinates {
				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
			};

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
		3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
		2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
	\end{tabular}

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		L1 Diff <= 0.82378 &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
	\end{tabular}

>>>>

	\hspace*{-10ex}
	\begin{tikzpicture}[scale=0.65]
		\begin{axis}[	axis on top, xlabel = \(x'_i\),
			ylabel = {\(y_i\)}, zlabel = \(\hat{y}_i\),
			set layers=default,
			xmax = 4, xmin = -4,
			ymax = 1, ymin = -1,		
			zmax = 1, zmin = -1,
			unit vector ratio=1 1 1, scale=2.5,  ytick   = {-1,0,1},
			yticklabels = {$-\gamma_i$,$0$,$\gamma_i$}, xtick = {0},
			xticklabels = {$0$}, ztick   = {-1,0,1},
			zticklabels = {$-\gamma_i$,$0$,$\gamma_i$},
			view={35}{14},
			]
			\addplot3[ fill=blue,opacity=0.1, fill opacity=0.4] 
			coordinates {
				(0,0,0) (-1,1,0) (-4,1,0) (-4,-1,0) (0,-1,0) (0,0,0)
			};

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                       0.01288 & 10608 \\\hline
		3v,open 100 &     0.040074 &  0.028934 &                      0.021441 & 10922 \\\hline
		3v,open 100 &     0.039824 &  0.028832 &                      0.022255 & 22153 \\\hline
		2v,open 100 &     0.046719 &  0.024364 &                      0.024436 & 10922 \\\hline
	\end{tabular}

@@

	\begin{tabular}{|l|l|l|l|l|}\hline
		$L_{1,diff}\leq 0.83$ &        Bound &  Solution &                          Real &  Time \\\hline
		1v,open 100 &     0.035613 &  0.035613 &                      0.019141 &   984 \\\hline
		3v,open 100 &     0.041382 &  0.025433 &                      0.016638 &  1082 \\\hline
		3v,open 100 &      0.03496 &  0.027206 &                      0.021607 & 14523 \\\hline
		3v,open 100 &     0.032906 &  0.027655 &                      0.016481 & 72126 \\\hline
		2v,open 100 &     0.041787 &  0.022805 &                      0.022882 &  1082 \\\hline
		2v,open 100 &     0.035964 &  0.023563 &                      0.023608 & 14523 \\\hline
	\end{tabular}
